---
title: "SydneyEnergyResearch"
subtitle: "Electricity"
author: "© University of Sydney 2023"
date: 30/03/2023
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    css: 
      - https://use.fontawesome.com/releases/v5.0.6/css/all.css
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readxl)
data2019 <- read_excel("data/Ausgrid average electricity consumption by LGA 201819.xlsx", range = "A1:Q40")
data2020 <- read_excel("data/Ausgrid average electricity consumption by LGA 2020.xlsx", range = "A2:Q43")
data2023 <- read_excel("data/Ausgrid average electricity consumption by LGA 202223 excel.xlsx", range = "A2:Q43")
```
Taking a quick view of the data
```{r eval=TRUE}
# For the 2019 data set
dim(data2019)
head(data2019, 10)
# For the 2020 data set
dim(data2020)
head(data2020, 10)
# For the 2023 data set
dim(data2023)
head(data2023, 10)
```
## Data source verification
This data source is from Ausgrid, which is a large electricity provider that has more than 1.7 million customers in Sydney, Australia.Although this is a electricty provider that is run by a company, however, it must be subjected to a range of regulations and guidelines to ensure the accuracy of their data, including the Australian Energy Regulator(AER), according to the Australian energy policies.

Some useful functions
```{r}
wrap.it <- function(x, len)
{ 
  sapply(x, function(y) paste(strwrap(y, len), 
                              collapse = "\n"), 
         USE.NAMES = FALSE)
}

wrap.labels <- function(x, len)
{
  if (is.list(x))
  {
    lapply(x, wrap.it, len)
  } else {
    wrap.it(x, len)
  }
}
```
## IDA
To get an idea of the new data, we will do a quick bargraph of the 'general supply' columns from the excel file.
(It is with several trial and error, that we have found out the original excel file is not suitable for R data analysis, therefore manual excel operation was done to extract it out into a form which was useful.)
```{r eval=TRUE}
library(readxl)
library(dplyr)
options(scipen = 999)

# Read in files
extracted_data <- read_excel("data/Electricity_consumption(extracted).xlsx")
extracted_data <- arrange(extracted_data)

# Setting up the output graph
par(mar = c(5, 8, 0, 2), mgp = c(4, 1, 0))

# The 2019 Dataset
values2019 <- extracted_data$`2019-R`
suburbs2019 <- extracted_data$H2019
barplot(values2019, names.arg=wrap.labels(rev(suburbs2019), 20), 
        col="red", xlab=" Electricity consumption/MWh", horiz=T, las=2, cex.names = 0.7)

# The 2020 Dataset
values2020 <- extracted_data$`2020-R`
suburbs2020 <- extracted_data$H2020
barplot(values2020, names.arg=wrap.labels(rev(suburbs2020), 20), 
        col="green", xlab=" Electricity consumption/MWh", horiz=T, las=2, cex.names = 0.7)

# The 2021 Dataset
values2021 <- extracted_data$`2021-R`
suburbs2021 <- extracted_data$H2021
barplot(values2021, names.arg=wrap.labels(rev(suburbs2021), 20), 
        col="blue", xlab=" Electricity consumption/MWh", horiz=T, las=2, cex.names = 0.7)
```
## Reseearch question 1:
What was the relationship 


## Research question 2:
During the pandemic, we observed several lockdowns where people were forced to stay home due to businesses shutting down, commercial buildings transitioning to a work from home environment.This meant there was a lot of changes with the distribution of the population, and the impact of this on electricity consumptions.
To get an general idea of which areas had the highest amount of electricity consumption, normal distribution graph was made.
(We'll use the latest complete dataset, which was the 2021 dataset)
General Supply
```{r eval=TRUE}
distribution <- function(title, name, values){
  df <- data.frame(label=name, value=values)
  df_sorted <- df[order(df$value, decreasing = FALSE),]
  mean_val <- mean(values)
  sd_val <- sd(values)
  par(mar = c(5, 6, 2, 2), mgp = c(4, 1, 0), fig = c(0, 1, 0, 1), fin = c(6, 4))
  barplot(df_sorted$value, names.arg=wrap.labels(df_sorted$label, 20), 
        col="blue", xlab=title, horiz=T, las=2, cex.names = 0.4, , cex.lab=0.7, cex.axis=0.7)
  hist(values, breaks=10, freq=FALSE, col="grey", xlab="Values", main="Normal Distribution")
  curve(dnorm(x, mean=mean_val, sd=sd_val), add=TRUE, col="blue")
  abline(v = mean_val, col = "red", lwd = 2)
}
distribution("Electricity Consumption/MWh", suburbs2021, values2021)
```
'Non-residential small-medium sites'
```{r eval=TRUE}
values2021M <- extracted_data$`2021-M`
distribution("Electricity Consumption/MWh",suburbs2021, values2021M)
```
'Non-residential large sites'
```{r eval=TRUE}
values2021L <- extracted_data$`2021-L`
distribution("Electricity Consumption/MWh",suburbs2021, values2021L)
```
Finally, to make a conclusion, a pie chart is made
```{r eval=TRUE}
par(mar = c(5, 6, 2, 2), mgp = c(4, 1, 0), fig = c(0, 1, 0, 1), fin = c(6, 4))
sum_2021G <- sum(values2021)
sum_2021M <- sum(values2021M)
sum_2021L <- sum(values2021L)
pie_values <- c(sum_2021G, sum_2021M, sum_2021L)
pie_labels <- c("General Supply", "Medium Sites", "Large Sites")
pie(pie_values, labels = pie_labels)
```
As can see, this shows a nuanced side of the distribution of electricity consumption by Ausgrid, as Ausgrid is the largest distributor of electricity on the east coast, there's a high chance that this represents the total electricity consumption of NSW.
If we're talking about large areas like shopping malls, business skyscrapers or tourist attractions, than population does matter, in fact a lot, so places where there tends to be large flow of population, like Sydney(The normal distribution graph shows how skewed this situation is), actually uses the most amount electrcity.
However, if we're talking about residential supplies, which corresponds to the 'General Supply' column of the data source.Than population matters less, because with residential usage, the amount of electricity consumption depends on the size of the housing, which is why I guess Central Coast has the most amount of electricity
(Note: Again, just to be cautious, it is considered that Ausgrid could've had a target customer base, which could explain part of this situation as well)

## References
jrara. (17 C.E., November). plot - R barplot: wrapping long text labels? Stack Overflow. https://stackoverflow.com/questions/20241065/r-barplot-wrapping-long-text-labels

